A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-10-29 paper/main.tex
Double-check label, copied from above.
Make more obvious that 3rd-level was mixed-effects

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors (see Table \ref{tab:regressors}) based on events drawn
from the annotation.
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to \texttt{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and modeled as a boxcar function from a
word's onset to offset.
% phonemes
The 80 most often occurring phonemes (\texttt{n} with N=6053 to \texttt{IY1}
with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and modeled as
boxcar function from a phoneme's onset to offset.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance correlating with sentence comprehension.
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
intervals without audible speech that lasted at least \unit[3.6]{s} \todo{why 3.6?}.
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s}\todo{why 1.8} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the average
length of phonemes.
% low-level nuisance regressors
Lastly, we used continuous bins of information about low-level auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with assumed low-level perceptual processes.
% convolving
Time series of events were convolved with FSL's ``Double-Gamma HRF'' as a model
of the hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix to compensate for
regional differences between modeled and actual HRF.
% motion parameters & temporal filtering of design motion parameter are
% filtered, too. See FSL manual: ``All (confound) EVs will be filtered to match
% the processing applied to the input data''
Finally, six motion parameters were used as additional nuisance regressors and
the design was subjected to the same temporal filtering as the BOLD time series.
% t-contrasts
The following three $t$-contrasts were defined: 1) words (all 21
\texttt{tag}-related regressors) > no-speech (\texttt{no-sp}),
% 1b) no-speech > words
2) proper nouns (\texttt{ne}) > coordinate conjunctions (\texttt{kon}), and
% 2b) coordinate conjunctions > proper nouns
3) nouns (\texttt{nn}) > coordinate conjunctions.
% 3b) coordinate conjunctions > nouns

@@

% 2nd lvl
The second-level analysis that averaged contrast estimates across the eight
stimulus segments per subject was carried out using a fixed effects model by
forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of
Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
% 3rd lvl
The third level analysis which averaged contrast estimates across subjects was
carried out using FLAME stage 1 with automatic outlier deweighting
\citep{woolrich2004multilevel, woolrich2008robust}.
% thresholding
Z (Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a corrected cluster significance threshold of p<.05
\citep{woolrich2008robust}.
% identification of brain regions
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.

>>>>

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors (see Table \ref{tab:regressors}) based on events drawn
from the annotation.
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to \texttt{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and modeled as a boxcar function from a
word's onset to offset.
% phonemes
The 80 most often occurring phonemes (\texttt{n} with N=6053 to \texttt{IY1}
with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and modeled as
boxcar function from a phoneme's onset to offset.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance correlating with sentence comprehension.
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
intervals without audible speech that lasted at least \unit[3.6]{s} \todo{why 3.6?}.
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s}\todo{why 1.8} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the average
length of phonemes.
% low-level nuisance regressors
Lastly, we used continuous bins of information about low-level auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with assumed low-level perceptual processes.
% convolving
Time series of events were convolved with FSL's ``Double-Gamma HRF'' as a model
of the hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix to compensate for
regional differences between modeled and actual HRF.
% motion parameters & temporal filtering of design motion parameter are
% filtered, too. See FSL manual: ``All (confound) EVs will be filtered to match
% the processing applied to the input data''
Finally, six motion parameters were used as additional nuisance regressors and
the design was subjected to the same temporal filtering as the BOLD time series.
% t-contrasts
The following three $t$-contrasts were defined: 1) words (all 21
\texttt{tag}-related regressors) > no-speech (\texttt{no-sp}),
% 1b) no-speech > words
2) proper nouns (\texttt{ne}) > coordinate conjunctions (\texttt{kon}), and
% 2b) coordinate conjunctions > proper nouns
3) nouns (\texttt{nn}) > coordinate conjunctions (\texttt{kon}).
% 3b) coordinate conjunctions > nouns

@@

% 2nd lvl
The second-level analysis that averaged contrast estimates across the eight
stimulus segments per subject was carried out using a fixed effects model by
forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of
Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
% 3rd lvl
The third level analysis which averaged contrast estimates across subjects was
carried out using a mixed-effects model (FLAME stage 1) with automatic outlier deweighting
\citep{woolrich2004multilevel, woolrich2008robust}.
% thresholding
Z (Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a corrected cluster significance threshold of p<.05
\citep{woolrich2008robust}.
% identification of brain regions
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
